---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

Introduction:

In the previous assignment, the effect of different variables on price per night was discussed. There are several other items that play a significant role in price per night. One of these items that has an important impact on the price for Airbnb places is surrounding area's conditions. For example, if you know a specific Airbnb is located in a place where deals with noise disturbance, how likely are you to book an Airbnb listing in this area? From my point of view, people prefer to stay in Airbnb places that are located in quiet and peaceful areas. Therefore, in this assignment, I am wondering if there are differences in price per night for Airbnb listings in quiet and noisy areas? To respond this question, in the following, the means of different groups are compared by t.test and anova.

Data Analysis:

For the first analysis, two groups are defined. The first group contains Airbnb listings, which are located in areas with noise problem and the second group includes Airbnb places, which are located in areas without noise disturbance reported. I use t.test to compare the means of these two groups to to find out if there are differences in their prices (with noise vs. without noise). To find areas, where deal with noise disturbance, I used CRM cases file, which includes received 311 requests in different places across Boston.


```{r}
Airbnb <- read.csv("~/Desktop/air_bnb copy.csv", sep = ",", header = TRUE, stringsAsFactors=FALSE)

Airbnb$price <- as.numeric(gsub('[$,]', '', Airbnb$price))

summary(Airbnb$price)
# Importing CRM Cases file
CRM_311 <- read.csv("~/Desktop/Big data for cities/CRM Cases 2015_2019 Unrestricted.csv", sep = ",", header = TRUE, stringsAsFactors=FALSE)
# Merging Airbnb file and CRM Cases file by blk_ID_10
Airbnb_CRM <- merge(Airbnb, CRM_311, by.x = 'Blk_ID_10', by.y = 'BLK_ID_10', all.x = TRUE)

# Defining noise variable
Airbnb_CRM$noise <- ifelse(Airbnb_CRM$REASON == "Noise Disturbance" | 
                             Airbnb_CRM$REASON == "Generic Noise Disturbance", 1, 0)
# t.test
t.test(price ~ noise, data = Airbnb_CRM)
```

According to the t.test, the mean for group 0, which is associated with Airbnb listings located in areas without noise disturbance, is about 173 and the mean for group 1, which is associated with Airbnb places located in areas with noise pollution, is about 162. Therefore, the difference between means of two groups is about 11. P-value is equal to 0.009, which indicates that there is a very small probability that this difference is due to chance. Therefore, there is evidence that places with noise reported show lower average price per night than places without noise disturbance. In fact, reporting noise problems in a street or neighborhood around an Airbnb listing, has negative impact on that Airbnb, because it leads to a drop in the price. Since p-value is less than 0.05, I reject the null hypothesis, which is the prices per night for Airbnb that is located in noisy area and the Airbnb that is located in quiet area are the same.


There are three types of noise disturbance, which are automotive noise disturbance, loud parties/music/people, and undefined noise. In the following, I try to compare price per night across different types of noises.


```{r}
# Defining noise types
Airbnb_CRM$noise_types <- ifelse(Airbnb_CRM$TYPE == "AUTOMOTIVE NOISE DISTURBANCE",'Automotive noise',
                                 ifelse(Airbnb_CRM$TYPE == "LOUD PARTIES/MUSIC/PEOPLE", 
                                                           'Loud parties/music/people', 
                                 ifelse(Airbnb_CRM$TYPE == "UNDEFINED NOISE DISTURBANCE", 
                                                            'Undefined noise', 'no noise')))
# Comparing the means of three groups
anova1 <- aov(price ~ noise_types, data = Airbnb_CRM)
TukeyHSD(anova1)
```

Based on the anova results, degrees of freedom (df-1 = 3) indicates that there are four groups. The between variance is 570,462 and the within variance is 19,121. The F statistic (between variance/within variance) is equal to 29.83. Since P-value is very small, we can conclude that there is a significant difference between the means of all groups.

According to TukeyHSD, there is a matrix of the differences between all the various noise types. For example, Loud parties/music/people minus Automotive noise is -135. It means that price per night is about $135 higher in areas with Automotive noise compared to areas that deal with Loud parties/music/people noise. If we consider p-value, we can conclude for instance, Undefined noise is significantly different from Automotive noise, having less price per night. However, Undefined noise has significantly higher price per night than areas with Loud parties/music/people noise and no noise areas. Therefore, since areas with reported noise have the lowest average price compared to quiet areas, we can conclude that Airbnb listings, which are located in areas with loud parties/music/people noises have lower prices. In fact, this kind of noise has the highest negative effect on price. In the following, the plot shows the mean for different types of noises.


```{r}
library(reshape2)
library(ggplot2)

# Melting the data frame to create means
melted <- melt(Airbnb_CRM[c(61,130)],id.vars=c("noise_types"))
means <- aggregate(value ~ noise_types, data=melted, mean)
names(means)[2]<-"mean"
# Adding standard errors
ses <- aggregate(value ~ noise_types, data = melted, 
                 function(x) sd(x, na.rm=TRUE)/sqrt(length(!is.na(x))))
names(ses)[2]<-'se'
means <- merge(means, ses, by='noise_types')
means <- transform(means, lower=mean-se, upper=mean+se)
means
# Plot to indicate means
base <- ggplot(data = means, aes(x = noise_types, y = mean)) +
  geom_bar(stat="identity",position="dodge", fill="pink") + ylab("Mean") + xlab("Types of noise")
k <- base + geom_errorbar(aes(ymax=upper, ymin=lower), position=position_dodge(.9)) + ggtitle( "Average of types of noise disturbance") + theme_bw()+ theme(text = element_text(size=14))
k
ggsave("k.png", path = "~/Desktop")
```

The results of the plot and table indicate that Automotive noise has the highest average of price and Loud parties/music/people has the lowest average among all types of noises. It means that if Automotive noise in a particular area is high, the average of price is higher compared to the area with loud parties/music/people noise. The difference between lower and upper bounds, which represents variation from standard error below the mean and standard error above the mean for all measures, indicates that Automotive noise has higher difference compared to other types of noises. These lower and upper bounds have the lowest value for no noise type.

Furthermore, I would like to know if there is a difference between number of reviews, which is considered as the number of people who booked an Airbnb place, and the score for reviews about location of Airbnb listing, for listings in noisy area and in quiet areas? Therefore, the below plot shows comparison of two different variables (number_of_reviews and review_scores_location) across four groups.

```{r}
# Compare two variables
melted <- melt(Airbnb_CRM[c(76,84,133)],id.vars=c("noise_types"))
means2 <- aggregate(value ~ noise_types + variable, data = melted, mean)
names(means2)[3]<-"mean"
ses2 <- aggregate(value ~ noise_types + variable, data = melted, 
                  function(x) sd(x, na.rm=TRUE)/sqrt(length(!is.na(x))))
names(ses2)[3]<-'se'
means2 <- merge(means2, ses2, by=c('noise_types','variable'))
means2 <- transform(means2, lower=mean-se, upper=mean+se)
means2
# Plot to represent means 
ggplot(data=means2, aes(x=noise_types, y=mean, fill=variable)) + 
  geom_bar(stat="identity",position="dodge") + 
  geom_errorbar(aes(ymax=upper, ymin=lower),position=position_dodge(.9)) + 
  ylab("Mean") + xlab("Types of noise") + theme(axis.text.x = element_text(angle = 90, size = 10))
```

The results of the above graph and table represent that if there is no noise in an area surrounding an Airbnb place, the number of reviews, which is considered as number of bookings will be increased. On the other hand, if there is Loud parties/music/people noise in an area that an Airbnb listing is located, the average of number of reviews and scores for reviews about location will be decreased. Moreover, if there is Automotive noise in an area, the average of score for reviews about location will be increased. We can conclude that most of the customers don't care about automotive noise.



The below graph shows number of Airbnb listings, which are located in the areas that have noise disturbance. The results show that South End contains the highest number of noise reports among all neighborhoods.

```{r}
count_nbhd
table(Airbnb_CRM$noise_types)
library(sqldf)
names(Airbnb_CRM)[110] <- 'type_noise'
Airbnb_CRM$noise_types2 <- ifelse(Airbnb_CRM$TYPE == "AUTOMOTIVE NOISE DISTURBANCE",1,
                                 ifelse(Airbnb_CRM$TYPE == "LOUD PARTIES/MUSIC/PEOPLE", 
                                                           2, 
                                 ifelse(Airbnb_CRM$TYPE == "UNDEFINED NOISE DISTURBANCE", 
                                                            3, 0)))


table(Airbnb_CRM$noise_types2)
n <- sqldf("select neighbourhood_cleansed,
            sum(noise_types2 == 1) as AUTOMOTIVE_NOISE_DISTURBANCE,
            sum(noise_types2 == 2) as LOUDPARTIES_MUSIC_PEOPLE,
            sum(noise_types2 == 3) as UNDEFINED_NOISE_DISTURBANCE
            from Airbnb_CRM
            group by neighbourhood_cleansed")


table(Airbnb_CRM$noise_types2)
n2 <- sqldf("select Blk_ID_10,
            sum(noise_types2 == 1) as AUTOMOTIVE_NOISE_DISTURBANCE,
            sum(noise_types2 == 2) as LOUDPARTIES_MUSIC_PEOPLE,
            sum(noise_types2 == 3) as UNDEFINED_NOISE_DISTURBANCE
            from Airbnb_CRM
            group by Blk_ID_10")



n2
write.csv(n2,"~/Desktop/n2.csv", row.names = FALSE)
library(ggplot2)
l <- ggplot(data=Airbnb_CRM, aes(x=neighbourhood_cleansed, y=noise, fill = noise_types, width=0.5)) + theme_bw()+
  geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, size = 12)) + ylab("Noise Disturbance")+xlab("Neighborhoods")+ ggtitle("Types of Noise Problem in Each Neighborhood") + labs(fill="Noise Types")
l
ggsave("l.png", path = "~/Desktop")

library(sf)
# Shapefile of neighborhoods in Boston
nbhd_geo <- st_read(dsn="~/Desktop/boston_neighborhood_shapefiles_iq5/boston_neighborhood_shapefiles_iq5.shp")
# Convert coordinate system
nbhd_geo <- st_transform(nbhd_geo, "+proj=longlat +datum=NAD83 +no_defs")
# Importing latent variables's file
n <- read.csv("~/Desktop/n.csv")
# Merging shapefile and latent variable's file
nbhd_geo <- merge(nbhd_geo, n, by.x='Name', by.y = 'neighbourhood_cleansed',all.x=TRUE)

# Strict Hosts
library(tmap) 
tmap_mode('view')
tm_shape(nbhd_geo) + tm_polygons(c('AUTOMOTIVE_NOISE_DISTURBANCE','LOUDPARTIES_MUSIC_PEOPLE','UNDEFINED_NOISE_DISTURBANCE') , palette=list("Oranges", "Purples", "Blues"), style = "jenks") +  tm_facets(nrow=1,ncol=3) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) 


library(sf)
# Shapefile of neighborhoods in Boston
blk_geo <- st_read(dsn="~/Desktop/drive-download-20191128T171645Z-001/BlocksBostonBARI.shp")
# Convert coordinate system
blk_geo <- st_transform(blk_geo, "+proj=longlat +datum=NAD83 +no_defs")
# Importing latent variables's file
n2 <- read.csv("~/Desktop/n2.csv")
# Merging shapefile and latent variable's file
blk_geo
blk_geo <- merge(blk_geo, n2, by.x='Blk_ID_10', by.y = 'Blk_ID_10',all.x=TRUE)

# Strict Hosts
library(tmap) 
tmap_mode('view')
tm_shape(blk_geo) + tm_polygons(c('AUTOMOTIVE_NOISE_DISTURBANCE','LOUDPARTIES_MUSIC_PEOPLE','UNDEFINED_NOISE_DISTURBANCE') , palette=list("Oranges", "Purples", "Blues"), style = "jenks") +  tm_facets(nrow=1,ncol=3) + tm_style('col_blind') + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) 

library(tidyverse)
Airbnb_Mat <- select(Airbnb_CRM, review_scores_rating, noise,price,point,unreasonable_price,room_type,number_of_reviews, season)
corMat <- cor(Airbnb_Mat, cbind(Airbnb_CRM$review_scores_rating, Airbnb_CRM$noise, use="pairwise.complete.obs"))
colnames(corMat) <- c("Rating", "Noise Disturbance")
stargazer(corMat, header = FALSE, type = "text", font.size = "small", no.space = TRUE)


Airbnb_CRM$satisfaction <- ifelse(Airbnb_CRM$satisfaction == "Satisfaction", 1, 0)
Airbnb_CRM$room_type <- ifelse(Airbnb_CRM$room_type == "Entire home/apt", 0, ifelse(Airbnb_CRM$room_type == "Private room" | Airbnb_CRM$room_type == "Shared room", 1, 2))
table(Airbnb_CRM$room_type)

p <- glm(satisfaction ~ noise + point + price + room_type + number_of_reviews + minimum_nights , data=Airbnb_CRM, family ="binomial")
suppressMessages(library(stargazer)) 
stargazer(p, type = "text", header = FALSE, single.row = TRUE,
          dep.var.labels = c("Rating"), covariate.labels = c("Noise Disturbance", "Hosts' Policies Point"),
omit.stat=c("LL","ser"),
title = "Multivariate Regression of Noise Disturbance on Rating")


table(Airbnb_CRM$noise)
table(Airbnb_CRM$noise_type)

b <- Airbnb_CRM[Airbnb_CRM$noise == 1,]
table(b$point)
```



Conclusion:

This has been very intersting to me to realize the factors/items that could affect the price of an specific Airbnb listing. Other than amenities, location, type of the place, number of bedrooms/bath, there are definitely other items that people may not be aware of. For instance, this is interesting for me that if a particular area has noise disturbance, the price of Airbnb places within that area would be affected or not. In this assignment, I compared two groups; the first one contains Airbnb places in noisy area and the second one includes Airbnb places in quiet areas. The results represented that Airbnb places, which are located in peaceful areas have higher prices. In addition, if the area surrounding an Airbnb place has loud parties/people/music noise disturbance, the price per night will be further decreased, compared to other types of noises. Also, the comparison of two variables, which are number of reviews and score review about location across all types of noises is discussed.



